\Large \bf Polyglots : Crossing Origins by Crossing Formats

### 2013-02-21 main.tex
responsible disclosure and new time stamp for test page
Again, minor edits

Cross-origin communication in Flash adheres to the same-origin policy. However, this is not a restriction, since
 Flash also supports cross-origin communication via  
cross-origin resource sharing. Using CORS, a web server can relax the SOP to allow access to specified content.
%As mentioned, the embedded Flash file inherits the origin of the document.
An attacker can set an allow-all cross-origin policy, such as in Listing~\ref{lst:crossdomain} 
that open up for two way communication.

@@

The affected vendors have been made aware of the
vulnerabilities. These vendors include Adobe (notified instantly after
discovering the security implications of polyglot PDFs)
%in late 2009
and the major browser vendors. We have also contacted the vulnerable
web sites from the top 100 Alexa list.

>>>>

Cross-origin communication in Flash adheres to the same-origin policy. However, this is not a restriction, since
 Flash also supports cross-origin communication via  
cross-origin resource sharing. Using CORS, a web server can relax the SOP to allow access to specified content.
%As mentioned, the embedded Flash file inherits the origin of the document.
An attacker can set an allow-all cross-origin policy, such as in Listing~\ref{lst:crossdomain}, 
that open up for two way communication.

@@

The affected vendors have been made aware of the
vulnerabilities. These vendors include Adobe (notified instantly after
discovering the security implications of polyglot PDFs)
%in late 2009
and the major browser vendors. We have also contacted the vulnerable
web sites from the top 100 Alexa list.
%
Following responsible disclosure, we refrain from providing the names of the vulnerable web sites.
